Deriving Multi-Headed Projective Dependency Parses \\ from Link Grammar Parses

### 2014-11-16 doc/LinksToDAG_final.tex
fixed the tables and charts of LinksToDAG_final.tex

%\documentclass[11pt]{article}
%\usepackage{acl2014}
\usepackage{times}
\usepackage{url}
\usepackage{latexsym}
\usepackage{amsmath}
\usepackage{xspace}
\usepackage{enumitem}
\usepackage[small]{caption}
\usepackage{longtable}

\usepackage[usenames,dvipsnames,svgnames,table]{xcolor}
\usepackage{soul}

\usepackage{algorithm}
\usepackage[noend]{algpseudocode}
\usepackage{graphicx}
\usepackage{caption}
\usepackage{subcaption}

@@

\begin{figure*}[ht!]
  \vspace{-6pt}
  \centering
  \input{figure/sentences.tikz}
  \input{figure/long_parses.tikz}
  %\input{figure/long_parse2.tikz}
  \caption{\small The blue upper edges show CoNLL gold dependency parses; the red lower edges show our oriented version of the link grammar parses. Edges are shown as dotted lines if they appear only in one parse. Edges are highlighted in orange if the child has multiple parents.  Edges that appear in both parses are solid lines, drawn thicker if the directions do not match.  Vertical edges have parent 0.  For 100 example parses, see Appendix~\ref{app:parses} at \url{http://tidyurl.com/LinksToDAG_supplement}.}
  \label{fig:parses}
  \vspace{-6pt}
\end{figure*}

\begin{table*}[ht]
% \renewcommand{\arraystretch}{1.2}    % more space between rows
\input{figure/sample_link_analysis_coarse_table.tex}
\caption{Our solution, i.e., our reconstruction of the ``intended'' direction for each link type in the English Link Grammar.  We also indicate the extent to which each of these link types (1) has a single dominant direction, (2) participates in multi-headed constructions, and (3) corresponds to CoNLL links of a predictable direction and type.  For space reasons, we show only the start of this table---the full table can be found in Appendix~\ref{app:linktypes} at \url{http://tidyurl.com/LinksToDAG_supplement}.}\label{tab:linktypes}
\end{table*}

@@

\renewcommand{\arraystretch}{1.2}    % more space between rows
\input{figure/link_analysis_coarse_table.tex}

>>>>

%\documentclass[11pt]{article}
%\usepackage{acl2014}
\usepackage{times}
%\usepackage{url}
%\usepackage{latexsym}
\usepackage{amsmath}
%\usepackage{xspace}
\usepackage{enumitem}
\usepackage[small]{caption}
\usepackage{longtable}

\usepackage[usenames,dvipsnames,svgnames,table]{xcolor}
%\usepackage{soul}

\usepackage{algorithm}
\usepackage[noend]{algpseudocode}
\usepackage{graphicx}
%\usepackage{caption}
\usepackage{subcaption}

@@

%\hspace*{-1.5in}
\begin{figure*}[ht!]

  \vspace{-6pt}
  \centering

  %\input{figure/sentences.tikz}

  \hspace*{-0.5in}
  \begin{subfigure}[b]{0.49\textwidth}
	\begin{dependency}
	  \begin{deptext}
		{\scriptsize DT} \& {\scriptsize NN} \& {\scriptsize MD} \& {\scriptsize RB} \& {\scriptsize RB} \& {\scriptsize VB} \& {\scriptsize VB} \& {\scriptsize IN} \& {\scriptsize NN} \& {\scriptsize .} \\
		the \& matter \& may \& never \& even \& be \& tried \& in \& court \& . \\
		- \& n-u \& v \& e \& e \& v \& v-d \& r \& n-u \& - \\
	  \end{deptext}
	  \deproot[edge above, edge style = {blue, dotted}]{3}{\small ROOT}
	  \depedge[edge below, edge style = {red, ultra thick}]{2}{3}{S}
	  \depedge[edge above, edge style = {blue, ultra thick}]{3}{2}{\small SBJ}
	  \depedge[edge above, edge style = {blue, dotted}]{3}{4}{\small ADV}
	  \depedge[edge above, edge style = {blue, dotted}]{3}{5}{\small ADV}
	  \depedge[edge below, edge style = {red, thick}]{3}{6}{I}
	  \depedge[edge above, edge style = {blue, thick}]{3}{6}{\small VC}
	  \depedge[edge above, edge style = {blue, dotted}, edge unit distance =1.5ex]{3}{10}{\small P}
	  \depedge[edge below, edge style = {red, thick}]{2}{1}{D}
	  \depedge[edge above, edge style = {blue, thick}]{2}{1}{\small NMOD}
	  \depedge[edge below, edge style = {red, thick}]{7}{8}{MV}
	  \depedge[edge above, edge style = {blue, thick}]{7}{8}{\small ADV}
	  \depedge[edge below, edge style = {orange, thick}]{6}{7}{P}
	  \depedge[edge above, edge style = {blue, thick}]{6}{7}{\small VC}
	  \depedge[edge below, edge style = {red, thick}]{8}{9}{J}
	  \depedge[edge above, edge style = {blue, thick}]{8}{9}{\small PMOD}
	  \deproot[edge below, edge style = {red, dotted}]{2}{W}
	  \deproot[edge below, edge style = {orange, ultra thick, dotted}]{7}{WV}
	  \deproot[edge below, edge style = {red, dotted}]{10}{X}
	  \depedge[edge below, edge style = {red, dotted}]{6}{4}{E}
	  \depedge[edge below, edge style = {red, dotted}]{6}{5}{E}
	\end{dependency}
  \end{subfigure}
  \hspace*{0.5in}\begin{subfigure}[b]{0.49\textwidth}
	\begin{dependency}
	  \begin{deptext}
		{\scriptsize DT} \& {\scriptsize NN} \& {\scriptsize NN} \& {\scriptsize VB} \& {\scriptsize RB} \& {\scriptsize VB} \& {\scriptsize DT} \& {\scriptsize NN} \& {\scriptsize .} \\
		the \& Paris \& bank \& does \& n't \& publish \& that \& figure \& . \\
		- \& b \& n \& v \& - \& v \& j-d \& n \& - \\
	  \end{deptext}
	  \deproot[edge above, edge style = {blue, dotted}]{4}{\small ROOT}
	  \depedge[edge below, edge style = {red, thick}]{3}{1}{D}
	  \depedge[edge above, edge style = {blue, thick}]{3}{1}{\small NMOD}
	  \depedge[edge below, edge style = {red, thick}]{3}{2}{AN}
	  \depedge[edge above, edge style = {blue, thick}]{3}{2}{\small NMOD}
	  \depedge[edge below, edge style = {red, thick}]{6}{8}{O}
	  \depedge[edge above, edge style = {blue, thick}]{6}{8}{\small OBJ}
	  \depedge[edge below, edge style = {red, ultra thick}]{3}{4}{S}
	  \depedge[edge above, edge style = {blue, ultra thick}]{4}{3}{\small SBJ}
	  \depedge[edge below, edge style = {red, thick}]{4}{5}{N}
	  \depedge[edge above, edge style = {blue, thick}]{4}{5}{\small VMOD}
	  \depedge[edge below, edge style = {orange, thick}]{4}{6}{I}
	  \depedge[edge above, edge style = {blue, thick}]{4}{6}{\small VC}
	  \depedge[edge above, edge style = {blue, dotted}, edge unit distance = 1.7ex]{4}{9}{\small P}
	  \depedge[edge below, edge style = {red, thick}]{8}{7}{D}
	  \depedge[edge above, edge style = {blue, thick}]{8}{7}{\small NMOD}
	  \deproot[edge below, edge style = {red, dotted}]{3}{W}
	  \deproot[edge below, edge style = {orange, ultra thick, dotted}]{6}{WV}
	  \deproot[edge below, edge style = {red, dotted}]{9}{X}
	\end{dependency}
  \end{subfigure}

  \hspace*{-1in}
  \input{figure/long_parses.tikz}

  %\input{figure/long_parse2.tikz}
  \caption{\small The blue upper edges show CoNLL gold dependency parses; the red lower edges show our oriented version of the link grammar parses. Edges are shown as dotted lines if they appear only in one parse. Edges are highlighted in orange if the child has multiple parents.  Edges that appear in both parses are solid lines, drawn thicker if the directions do not match.  Vertical edges have parent 0.  For 100 example parses, see Appendix~\ref{app:parses} at \url{http://tidyurl.com/LinksToDAG_supplement}.}
  \label{fig:parses}
  \vspace{-6pt}

\end{figure*}

\begin{table*}[ht]
% \renewcommand{\arraystretch}{1.2}    % more space between rows
\hspace*{-1in}
\input{figure/sample_link_analysis_coarse_table.tex}
\caption{Our solution, i.e., our reconstruction of the ``intended'' direction for each link type in the English Link Grammar.  We also indicate the extent to which each of these link types (1) has a single dominant direction, (2) participates in multi-headed constructions, and (3) corresponds to CoNLL links of a predictable direction and type.  For space reasons, we show only the start of this table---the full table can be found in Appendix~\ref{app:linktypes} at \url{http://tidyurl.com/LinksToDAG_supplement}.}\label{tab:linktypes}
\end{table*}

@@

%\begin{table*}[ht]
%\renewcommand{\arraystretch}{1.2}    % more space between rows
%\hspace*{-1in}
\input{figure/link_analysis_coarse_table.tex}
%\end{table*}
